Implementing XBF: An Efficient Self-Describing Binary Format

### 2023-08-10 docs/paper.tex
Add microtype package
Update author section

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xurl}
\usepackage{xcolor}
\usepackage{listings}

@@

\author{
	\IEEEauthorblockN{David Krauthamer}
	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
		\textit{name of organization (of Aff.)}\\
		City, Country \\
		dkrautha@pm.me}
	\and
	\IEEEauthorblockN{Dov Kruger}
	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
		\textit{name of organization (of Aff.)}\\
		City, Country \\
		email address or ORCID}
	% \and
	% \IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
	% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
	% 	\textit{name of organization (of Aff.)}\\
	% 	City, Country \\
	% 	email address or ORCID}
}

>>>>

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xurl}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{microtype}

@@

\author{
	\IEEEauthorblockN{David Krauthamer}
	\IEEEauthorblockA{\textit{Electrical and Computer Engineering Department} \\
		\textit{Stevens Institute of Technology}\\
		Hoboken, USA \\
		dkrautha@pm.me}
	\and
	\IEEEauthorblockN{Dov Kruger}
	\IEEEauthorblockA{\textit{Electrical and Computer Engineering Department} \\
		\textit{Stevens Institute of Technology}\\
		Hoboken, USA \\
		dkruger@stevens.edu}
}
